### 2017-02-14 CS798-ConvexityAndOptimization/assignments/assignment_01.tex
Conv Opt A1 q4

\end{document}

>>>>

%Q4
\section{}
\paragraph{}
Let $P = \{ x| Ax \leq b\}$ be a polytope, where $A \in \R^{m\times n}$, $b \in \R^m_{>0}$. Let $a_i$ denote the $i$-th row of $A$. Let $[m] = \{1,\dots, m\}$. Let $C = \text{conv} \{\frac{a_i}{b_i} : i\in [m]\}$ be the convex hull of $\frac{a_i}{b_i}$'s. We want to show that $P^* = C$, where $P^*$ denotes the polar set of $P$.
\paragraph{}
We will use the theorem from class that $P^{**} = P$. With this theorem it is equivalent to show that $P = C^*$. First we will rewrite $P$ as $P = \{x| a_i^Tx \leq b_i \forall i\in[m]\}$. Observe that 
$$C^* := \{ x: x^Ty \leq 1\forall y \in C\}.$$
Observe that $\forall y \in C$ there exists $\lambda_i$ for $i\in [m]$ such that $y = \sum_{i\in[m]} \lambda_i \frac{a_i^T}{b_i}$, $\sum_{i\in [m]}\lambda_i = 1$, and $\lambda \geq 0$. This is the definition of convex hull. Hence substituting into our definition of $C^*$ we see
$$C^* = \{x : x^T(\sum_{i} \lambda_i \frac{a_i^T}{b_i}) \leq 1,\ \forall \lambda \geq 0, \sum_i \lambda_i = 1\}.$$
Rewriting slightly this is equivalent to
$$C^* = \{x : \sum_{i}\lambda_i \frac{a_i}{b_i}x \leq 1,\ \forall \lambda \geq 0, \sum_i\lambda_i = 1\}.$$
It is not hard to see that such $C^* = P$. We will write it out formally below for the sake of completeness.
\paragraph{}
Let $x\in C^*$. Then if we for each $i \in [m]$ define the vector $\lambda^i$ as
$$\lambda^i_j = \begin{cases}
1, &i=j \\
0, &i\neq j.
\end{cases}$$
Then $\lambda^i \geq 0$ and $\sum_j \lambda^i_j = \lambda^i_i = 1$. Since $x \in C$ we have
$$\sum_{j}\lambda^i_j \frac{a_j}{b_j} x \leq 1$$
and hence
$$\frac{a_i}{b_i} x \leq 1.$$
Thus for all $i \in [m]$, $a_i x\leq b_i$ ($b_i > 0$ implies inequality does not change order) and therefore $x \in P$. Now if we let $x\in P$, and let $\lambda \geq 0$ such that $\sum_i \lambda_i = 1$ then we need to show that $\sum_i \lambda_i \frac{a_i}{b_i} x \leq 1$. Since $x \in P$, $a_i x \leq b_i$ for all $i \in [m]$. Dividing by $b_i$ and multiplying by $\lambda_i \geq 0$ we obtain
$$\lambda_i\frac{a_i}{b_i} x \leq \lambda_i \quad \forall i \in [m].$$
Summing these inequalities over $i\in[m]$ obtains the desired bound:
$$\sum_i \lambda_i \frac{a_i}{b_i}x \leq \sum_i \lambda_i = 1.$$
Thus $P= C^*$ and by our theorem, $P^* = C^{**} = C$. $\blacksquare$
\end{document}
